Instructions for \confname{} Proceedings

### 2019-05-16 papers/EMNLP2019/analysis.tex
comments on analysis, points to highlight

@@

For measuring \textbf{instance-level agreement}, we consider all names annotated for an object as a response set and then average over these response sets. Furthermore, we compute \textbf{class-level agreement} by merging the response sets for all objects that have the same synset (given for the original VisualGenome name) and compute the measures over these aggregated response sets.
%\gbt{I'd call it ``name-level agreement'' -- it's not really category, is it?}
%\cs{@Sina (referring to our discussion we've had) object class instead of category would imo be indeed clearer here}

>>>>

\gbt{Points to discuss in the paper, as discussed with Carina May 16:}

\begin{itemize}
\item Super high variance in the agreement. Higher agreement for instances, lower for classes. Suggests systematicities at the instance level that do not depend on the class. Hypothesis, supported by qualitative analysis (Figure 3): relevance of visual perceptual factors. E.g.: saliency, background/foreground (desk-keyboard; bridge-train); ``angle'' from which the object is shown (see girl-t-shirt example); \dots In addition, we also find aspects discussed by Psycholing, but at the level of the instance: Typicality (see truck-bus example, bridge-dock, bench-seat). 
\item Forget about WordNet.
\item Implications for lang\&vision: 1) synset classification won't do (if the goal is to predict/label an object); 2) name classification won't do either; 3) ``mistakes'' done by models are also done by humans -- role of referential uncertainty.
\end{itemize}

@@

For measuring \textbf{instance-level agreement}, we consider all names annotated for an object as a response set and then average over these response sets. Furthermore, we compute \textbf{class-level agreement} by merging the response sets for all objects that have the same synset (given for the original VisualGenome name) and compute the measures over these aggregated response sets.
\gbt{@Sina, what are the synsets that you got here? Are they collection nodes, or the synset of the VG name as annotated in VG?}
